---
title: "Exploring and Tagging Text"
author: "Ruxin Liu"
date: "11/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyverse)
```

# Introduction:
 
  In this assignment, we used the tnum package to explore and tag text from Pride
  and Prejudice by Jane Austen.
  
  
```{r}
# Install the package
# devtools::install_github("truenumbers/tnum/tnum")
library(tnum)
# Get access to the database
tnum.authorize()
```

```{r}
# Explore the text in the Pride and Prejudice
tax1 <-tnum.getDatabasePhraseList("subject", levels = 3)
tax1
```

```{r}
num1 <- tnum.query("*pride* has count:word", max = 5050)
num1_df <- tnum.objectsToDf(num1)
num2 <- tnum.query("*pride* has text")
num2_df <- tnum.objectsToDf(num2)
```

```{r}
word_data <- data.frame(ch = ch_num_df(num1_df), para = para_num_df(num1_df), num = num1_df$numeric.value)
word_data <- word_data %>% 
  group_by(ch) %>% 
  summarise(count = sum(num))
```

```{r}
ggplot(data = word_data, aes(x= as.factor(ch), y = count, group=1)) +
  geom_line(color = "orange") +
  geom_point() +
  labs(x = "Chapter Number", y = "Number of Words") +
  ggtitle("Word Count In Each Chapter") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(axis.text = element_text(size = 7)) 
```



# Tag: love

  Since Pride and Prejudice is a romantic novel, the first word coming to my mind is love, and therefore, the love tag is added. It turns out that the word "love" has appeared in the book 111 times. 

  Below we showed a phrase graph by using tnum package.
  
```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"love\")", "reference:love")
love <- tnum.query("*pride* has text = REGEXP(\"love\")", max = 150) 
love_df <- tnum.objectsToDf(love)
# View(love_df)
piclove <- tnum.makePhraseGraphFromPathList(love_df$subject)
tnum.plotGraph(piclove)
```

## Creating Functions For Chapter Number


```{r}
# For query
ch_num <- function(query) {
  n <- length(query)
  vector <- rep(0, n)
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(tnum.getAttrFromList(query[i], "subject"), "[:/]")[[1]][4], 9))
  }
  return(vector)
}
```

```{r}
# For data frame
ch_num_df <- function(df) {
  n <- nrow(df)
  vector <- rep(0, n)
  subject <- df$subject
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(subject[i], "[:/]")[[1]][4], 9))
  }
  return(vector)
}
```


## Creating Functions For Paragraph Number

```{r}
# For query
para_num <- function(query) {
  n <- length(query)
  vector <- rep(0, n)
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(tnum.getAttrFromList(query[i], "subject"), "[:/]")[[1]][5], 11))
  }
  return(vector)
}
```

```{r}
# For data frame
para_num_df <- function(df) {
  n <- nrow(df)
  vector <- rep(0, n)
  subject <- df$subject
  for(i in 1 : n) {
    vector[i] <- as.numeric(substring(str_split(subject[i], "[:/]")[[1]][5], 11))
  }
  return(vector)
}
```

  We also showed a distribution plot by using ggplot package, which presents the appearance frequency of the word "love" in different chapters and paragraphs. And it is interesting but not surprising to see that the word "love" occurs relatively more often towards the end, where the story is approaching the happy ending. 
  
```{r}
love_data <- data.frame(ch = ch_num(love), para = para_num(love))
ggplot(love_data, aes(ch)) +
  geom_histogram(aes(fill = as.factor(para)), binwidth = 1)+
  labs(title = "Distribution of The Word Love")+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Paragraph Number") +
  xlab("Chapter Number")
```


# Tag: marry

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"marry\")", "reference:marry")
marry <- tnum.query("*pride* has text = REGEXP(\"marry\")", max = 60) 
marry_df <- tnum.objectsToDf(marry)
#View(marry_df)
picmarry <- tnum.makePhraseGraphFromPathList(marry_df$subject)
tnum.plotGraph(picmarry)
```

 
```{r}
marry_data <- data.frame(ch = ch_num(marry), para = para_num(marry))
ggplot(marry_data, aes(ch)) +
  geom_histogram(aes(fill = as.factor(para)), binwidth = 1)+
  labs(title = "Distribution of The Word Marry")+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Paragraph Number") +
  xlab("Chapter Number")
```


# Three major male characters: Darcy, Bingley & Wickhamn

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Darcy\")", "reference:Darcy")
Darcy <- tnum.query("*pride* has text = REGEXP(\"Darcy\")", max = 400) 
```

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Bingley\")", "reference:Bingley")
Bingley <- tnum.query("*pride* has text = REGEXP(\"Bingley\")", max = 310) 
```

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Wickham\")", "reference:Wickham")
Wickham <- tnum.query("*pride* has text = REGEXP(\"Wickham\")", max = 190) 
```

```{r}
Darcy_n <- ch_num(Darcy)
Bingley_n <- ch_num(Bingley)
Wickham_n <- ch_num(Wickham)
```

```{r}
Darcy_table <- as.data.frame(table(Darcy_n))
Bingley_table <- as.data.frame(table(Bingley_n))
Wickham_table <- as.data.frame(table(Wickham_n))
```


```{r}
ggplot() +
  geom_path(data = Darcy_table, aes(x= as.numeric(Darcy_n), y = as.numeric(Freq), color = "red")) +
  geom_point(data = Darcy_table, aes(x= as.numeric(Darcy_n), y = as.numeric(Freq), color = "red")) +
  geom_path(data = Bingley_table, aes(x= as.numeric(Bingley_n), y = as.numeric(Freq), color = "blue")) +
  geom_point(data = Bingley_table, aes(x= as.numeric(Bingley_n), y = as.numeric(Freq), color = "blue")) +
  geom_path(data = Wickham_table, aes(x= as.numeric(Wickham_n), y = as.numeric(Freq), color = "green")) +
  geom_point(data = Wickham_table, aes(x= as.numeric(Wickham_n), y = as.numeric(Freq), color = "green")) +
  labs(x = "Chapter Number", y = "Frequency") +
  scale_color_identity(name = "Character name",
                          breaks = c("red", "blue", "green"),
                          labels = c("Darcy", "Bingley", "Wickham"),
                          guide = "legend")
```

# Tag: where Darcy and Elizabeth co-occur

```{r}
tnum.tagByQuery("*pride* has text = REGEXP(\"Elizabeth\")", "reference:Elizabeth_co")
Elizabeth <- tnum.query("*pride* has text = REGEXP(\"Elizabeth\")", max = 610) 
Elizabeth_df <- tnum.objectsToDf(Elizabeth)
tnum.tagByQuery("*pride* has text = REGEXP(\"Darcy\")", "reference:Darcy_co")
Darcy_co <- tnum.query("*pride* has text = REGEXP(\"Darcy\")", max = 400) 
Darcy_co_df <- tnum.objectsToDf(Darcy_co)
```


  Since we are working with a data frame, by using the dplyr package, we could find where our tag: Elizabeth_co occurs in the data frame: Darcy_co_df
  
```{r}
co_occur <- dplyr::filter(Darcy_co_df, grepl('reference:Elizabeth_co', tags))
co_ch <- ch_num_df(co_occur)
co_para <- para_num_df(co_occur)
```
  
  
```{r}
co_data <- data.frame(ch = co_ch, para = co_para)
ggplot(marry_data, aes(ch)) +
  geom_histogram(aes(fill = as.factor(para)), binwidth = 1)+
  labs(title = "Distribution of The Co-occurrence of Darcy and Elizabeth")+
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(fill = "Paragraph Number") +
  xlab("Chapter Number")
```

# Suggestions for Tnum package
  
  